Skill estimation using TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-04-29 doc/article.tex
Add bib files, and gitignore
Acknowledgments

% \en{We thank the anonymous reviewers for their helpful feedback.}
% \es{Agradecemos a revisores anónimos por su valiosos aportes.}
%
\en{Special thanks to Heungsub Lee for having published the basic TrueSkill model in Python \cite{lee-trueskill}.}
\es{Agradecemos especialmente a Heungsub Lee por haber publicado el modelo básico de TrueSkill en Python \cite{lee-trueskill}.}
% https://github.com/sublee/trueskill/issues/14
\en{We also thank Matias Mazzanti for constructive discussions during the implementation of the method.}
\es{También agradecemos a Matias Mazantti por las discusiones constructivas durante la implementación del método.}
%
\en{This work is supported by Universidad de Buenos Aires (UBACyT \todo{ubacyt}), CONICET (\todo{conicet}), and ANPCyT (\todo{ANPCyT}).}
\es{Este trabajo fue apoyado por la Universidad de Buenos Aires (UBACyT \todo{ubacyt}), CONICET (\todo{conicet}), and ANPCyT (\todo{ANPCyT}).}

@@

\bibliography{../../bibliografia/journalsAbbr,../../bibliografia/Gaming/gaming}
% All references should be made with \verb|\cite|, \verb|\citet|, \verb|\citep|,
% \verb|\citealp|
% \begin{itemize}
%   \item JSS-specific markup (\verb|\proglang|, \verb|\pkg|, \verb|\code|) should
%     be used in the references.
%   \item Titles should be in title case.
%   \item Journal titles should not be abbreviated and in title case.
%   \item DOIs should be included where available.
%   \item Software should be properly cited as well. For \proglang{R} packages
%     \code{citation("pkgname")} typically provides a good starting point.
% \end{itemize}
% \end{leftbar}
%

>>>>

% \en{We thank the anonymous reviewers for their helpful feedback.}
% \es{Agradecemos a revisores anónimos por su valiosos aportes.}
%
\en{Special thanks to Heungsub Lee for having published the basic TrueSkill model in Python \cite{lee-trueskill}.}
\es{Agradecemos especialmente a Heungsub Lee por haber publicado el modelo básico de TrueSkill en Python \cite{lee-trueskill}.}
% https://github.com/sublee/trueskill/issues/14
\en{We also thank Matias Mazzanti for constructive discussions during the implementation of the method.}
\es{También agradecemos a Matias Mazantti por las discusiones constructivas durante la implementación del método.}
%
\en{This work is supported by Universidad de Buenos Aires and CONICET}
\es{Este trabajo fue apoyado por la Universidad de Buenos Aires y CONICET.}

@@

\bibliography{journalsAbbr,gaming}
% All references should be made with \verb|\cite|, \verb|\citet|, \verb|\citep|,
% \verb|\citealp|
% \begin{itemize}
%   \item JSS-specific markup (\verb|\proglang|, \verb|\pkg|, \verb|\code|) should
%     be used in the references.
%   \item Titles should be in title case.
%   \item Journal titles should not be abbreviated and in title case.
%   \item DOIs should be included where available.
%   \item Software should be properly cited as well. For \proglang{R} packages
%     \code{citation("pkgname")} typically provides a good starting point.
% \end{itemize}
% \end{leftbar}
%
